---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# easyweb

<!-- badges: start -->
<!-- badges: end -->

The goal of easyweb is to help you get started with making your [RMarkdown website](https://bookdown.org/yihui/rmarkdown/rmarkdown-site.html). It uses a two column table with some information about you in order to build a website that you can edit and polish later following instructions from [Emily Zabor](http://www.emilyzabor.com/tutorials/rmarkdown_websites_tutorial.html) and from [here](https://robertmitchellv.com/blog-building-site-with-rmarkdown.html).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("ComunidadBioInfo/easyweb")
```
## Example

Here is an example table with the information that `easyweb::easyweb()` requires in order to get you started with your website.

```{r example}
library(easyweb)

## Example easyweb table
options(width = 200)
easyweb_example
```

Next, you can save this object into a tab-separated table and use it as input for `easyweb::easyweb()` which will build your website in the specified `path`.

```{r build_website, eval = FALSE}
## Create an example website directory where the files will be saved
example_website_path <- file.path(tempdir(), 'easyweb')
dir.create(example_website_path, showWarnings = FALSE)
example_tsv <- file.path(example_website_path, 'web.tsv')

## Save the example table as a file
write.table(easyweb_example, file = example_tsv, sep = '\t',
    quote = FALSE, row.names = FALSE)

## Build the website
easyweb(example_tsv, path = example_website_path, overwrite = TRUE)
```

